---
title: "Assignment4"
author: "Adhil"
date: '2022-06-14'
output: 
  html_document: 
    df_print: kable
    theme: darkly
    toc: yes
    toc_float: yes
---
<style>
#TOC {
  font-size: 16px;
  font-family: roboto, verdana;
  color: cyan; 
}
p {
    font-size: 18px;
    font-family: Bookman Old Style;
    line-height: 24px;
    margin: 0px 0px 12px 0px;
}

h1 {
    text-align: center;
    font-family: roboto;
    font-size: 24px;
    font-weight: bold;
    color: lightgreen;
}

h2, h3, h4, h5, h6, legend {
    font-family: Bookman Old Style;
    font-size: 18px;
    font-weight: bold;
    color: cyan;
}

</style>

#Loading data...
```{r , warnings = FALSE, message = FALSE,  comment=""}

absents = read.csv("F:/Rappo/Data Sheets/Absenteeism_at_work.csv")
require(dplyr)
###Check whether NA is available or not###
f1 = which(is.na(absents))
f1
```


#Nature of variable
```{r , warnings = FALSE, message = FALSE,  comment=""}

str(absents)
```


#Transforming Nature of the variables
```{r , warnings = FALSE, message = FALSE,  comment=""}

absents$Seasons = as.factor(absents$Seasons)
absents$Social.smoker = as.factor(absents$Social.smoker)
absents$ID = as.factor(absents$ID)
absents$Social.drinker = as.factor(absents$Social.drinker)
absents$Reason.for.absence = as.factor(absents$Reason.for.absence)
absents$Month.of.absence = as.factor(absents$Month.of.absence)
absents$Month.of.absence = as.factor(absents$Month.of.absence)
absents$Disciplinary.failure = as.factor(absents$Disciplinary.failure)
absents$Day.of.the.week = as.factor(absents$Day.of.the.week)


```


#Rename variables
```{r , warnings = FALSE, message = FALSE,  comment=""}

absents2 = absents %>%  rename(Sons = Son )
```


# Find suitable univariate summaries
```{r , warnings = FALSE, message = FALSE, comment=""}




```

We have found out the factors that affect the the increase in the absentees
the increase in transport expenses increases the absentees by 3%
* The Distance from home to work increses absentees by 9%
* If service time increase by 2% absentees also increase by 2%
* The more the number of children the employee has the more the employee takes a
day off
* The Person who is a smoker and a drinker has a high risk of being absent for a long time period


# Find the required Correlation for grouped and ungrouped
```{r , warnings = FALSE, message = FALSE,  comment=""}
d13=absents %>% group_by(Seasons,Absenteeism.time.in.hours) %>% summarise(CNT=n()) %>%  mutate(PERC=round(100*CNT/nrow(absents),2))

d11 = absents %>% group_by(Reason.for.absence, Absenteeism.time.in.hours) %>% summarise(mean = mean(Absenteeism.time.in.hours), ctt = n())

```
1. In the first Season 30 people are absent by 2 hours 
1. Twenty nine people are absent by 4 hours in the first season
1. The time of absenteeism is high for diseases of the circulatory system
1. The cause due to 23 and 28 are alarmingly high



